Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Kind of funny typo

The issue is not as bad as it sounds: the system presented
in~\cite{RootCauseOfBlame} actually corresponds to the wished, stronger
semantics in practice. The specification is just not exactly the right one, but
this can probably be fixed along the lines
of~\ref{KeilThiemannUnionIntersection}, where the notion of context used to
define satisfaction is carefully restricted (\emph{elimination contexts}). While
this kind of oversight doesn't lower the quality of the work
of~\ref{RootCauseOfBlame} by any measure, it illustrates that contract
satisfaction in presence of unions, intersections and functions is a tricky
notion. This difficulty contrasts with the standard framework of higher-order
contracts where satisfaction is much more straightforward.
% Next, we can combine these two contexts into one, that essentially
% has one single missing value, that will be used independently in both contexts
% from Figure \ref{fig:valid-contexts}, as shown on Figure \ref{fig:invalid-context}.
% This context is not a valid \nickel{Num -> Num} context, since it will apply
% the value put on $\square$ (through \nickel{f}) to a non \nickel{Num} (\nickel{true}).
% In a similar way, it is not a valid \nickel{Bool -> Bool} context either.
% Therefore, according to the semantics from the Williams, Morris, and Wadler paper, as
% shown on Figure \ref{fig:wmw-semantics}, it is not a valid
% \nickel{Num -> Num @& Bool -> Bool} context.

>>>>

The issue is not as bad as it sounds: the system presented
in~\cite{RootCauseOfBlame} actually corresponds to the wished, stronger
semantics in practice. The specification is just not exactly the right one, but
this can probably be fixed along the lines
of~\cite{KeilThiemannUnionIntersection}, where the notion of context used to
define satisfaction is carefully restricted (\emph{elimination contexts}). While
this kind of oversight doesn't lower the quality of the work
of~\cite{RootCauseOfBlame} by any measure, it illustrates that contract
satisfaction in presence of unions, intersections and functions is a tricky
notion. This difficulty contrasts with the standard framework of higher-order
contracts where satisfaction is much more straightforward.
% Next, we can combine these two contexts into one, that essentially
% has one single missing value, that will be used independently in both contexts
% from Figure \ref{fig:valid-contexts}, as shown on Figure \ref{fig:invalid-context}.
% This context is not a valid \nickel{Num -> Num} context, since it will apply
% the value put on $\square$ (through \nickel{f}) to a non \nickel{Num} (\nickel{true}).
% In a similar way, it is not a valid \nickel{Bool -> Bool} context either.
% Therefore, according to the semantics from the Williams, Morris, and Wadler paper, as
% shown on Figure \ref{fig:wmw-semantics}, it is not a valid
% \nickel{Num -> Num @& Bool -> Bool} context.
